Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-07 paper/sec-mva.tex
work on mva section

Our final results are summarized in Table, where we indicate
the value of the optimal cut in each category,
the number of signal and background events $N_{\rm ev}$,
and also $S/\sqrt{B}$ and $S/B$.
%
For completeness, we also include the results after the cut-based
analysis.
%
Given that the signal significance is much larger in the boosted as
compared to the other two categories, no additional information
could be obtained by combining the significance of the three
categories, and it seems more efficient to perform
the analysis exclusively in the boosted category.

>>>>

Our final results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
the value of the optimal cut in each category,
the number of signal and background events $N_{\rm ev}$,
and also $S/\sqrt{B}$ and $S/B$.
%
For completeness, we also include the results after the cut-based
analysis.
%
Given that the signal significance is much larger in the boosted as
compared to the other two categories, no additional information
could be obtained by combining the significance of the three
categories, and it seems more efficient to perform
the analysis exclusively in the boosted category.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Boosted category}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
      193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$  &  &  &  & \\
        \hline
  \end{tabular}
   $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Intermediate category}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
      660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ &  &  &  & \\
        \hline
  \end{tabular}
    $\,$\\
  \vspace{0.4cm}
  \noindent
  \begin{tabular}{c|c|c|c||c|c|c|c}
    \hline
    \multicolumn{8}{c}{Resolved category}\\
    \hline
    \hline
    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
    \hline
    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
        Signal & Back   &     &   &  Signal & Back   &     &    \\
    \hline
      $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$   &  &  &  & \\
        \hline
  \end{tabular}
  \caption{\small The results for the number of signal and
    background events
    at the HL-LHC for both the cut-based analysis and after the
    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
    values in the two cases.
    %
    From top to bottom we show the results for boosted,
    intermediate and resolved categories.
    %
    Note that the optimal value of the MVA cut
    is different in each of the three categories.
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
